# Results

```{r results, echo=F, message=F, warning=F}
  # Use pandoc for Word documents
  format="latex"

  library(tidyverse)
  library(readr)
  library(knitr)
  library(kableExtra)
  library(broom) # https://cran.r-project.org/web/packages/broom/vignettes/broom.html

  satiated_data <- read_csv("data/SATIATED-Results - Sheet1.csv")
  
  
  demographics <- satiated_data %>%
  group_by(randomseq) %>%
  summarise(
    total = n(),
    intubation_attempts_past_12_months = median(intattempts),
    IQR_intubation_attempts_past_12_months = paste(fivenum(intattempts)[2],fivenum(intattempts)[4],sep="-"),
    max_intubation_attempts_past_12_months = max(intattempts),
    successful_intubation_attempts_past_12_months = median(succintattempt),
    IQR_successful_intubation_attempts_past_12_months = paste(fivenum(succintattempt)[2],fivenum(succintattempt)[4],sep="-"),
    max_successful_intubation_attempts_past_12_months = max(succintattempt),
    years_as_paramedic = median(yearsqualify),
    IQR_years_as_paramedic = paste(fivenum(yearsqualify)[2],fivenum(yearsqualify)[4],sep="-"),
    familiar_SALAD_technique = sum(familiarSALAD == "yes"),
    used_SALAD_in_last_3_months = sum(usedSALAD == "yes")
  )


demographicsTotal <- satiated_data %>%
  summarise(
    randomseq = "Total",
    total = n(),
    intubation_attempts_past_12_months = median(intattempts),
    IQR_intubation_attempts_past_12_months = paste(fivenum(intattempts)[2],fivenum(intattempts)[4],sep="-"),
    max_intubation_attempts_past_12_months = max(intattempts),
    successful_intubation_attempts_past_12_months = median(succintattempt),
    IQR_successful_intubation_attempts_past_12_months = paste(fivenum(succintattempt)[2],fivenum(succintattempt)[4],sep="-"),
    max_successful_intubation_attempts_past_12_months = max(succintattempt),
    years_as_paramedic = median(yearsqualify),
    IQR_years_as_paramedic = paste(fivenum(yearsqualify)[2],fivenum(yearsqualify)[4],sep="-"),
    familiar_SALAD_technique = sum(familiarSALAD == "yes"),
    used_SALAD_in_last_3_months = sum(usedSALAD == "yes")
  )

  demofinal <- t(rbind(demographics, demographicsTotal, make.row.names=F, stringsAsFactors=F))
  demofinal2 <- data.frame(demofinal, stringsAsFactors = F)
  colnames(demofinal2) <- c("AAB", "ABB", "Total")
  demofinal <- demofinal2
  
  finaldemodf <- data.frame(
    Measure = c("n", "Median intubation attempts in past 12 months (IQR)", "Median number of successful intubation attempts in past 12 months (IQR)", "Median years as paramedic (IQR)", "Familiar with SALAD technique"),
    AAB = c(demofinal$AAB[2], paste0(demofinal$AAB[3]," (",demofinal$AAB[4],")"), paste0(demofinal$AAB[6]," (",demofinal$AAB[7],")"), paste0(demofinal$AAB[9]," (",demofinal$AAB[10],")"), demofinal$AAB[11]),
    ABB = c(demofinal$ABB[2], paste0(demofinal$ABB[3]," (",demofinal$ABB[4],")"), paste0(demofinal$ABB[6]," (",demofinal$ABB[7],")"), paste0(demofinal$ABB[9]," (",demofinal$ABB[10],")"), demofinal$ABB[11]),
    Total = c(demofinal$Total[2], paste0(demofinal$Total[3]," (",demofinal$Total[4],")"), paste0(demofinal$Total[6]," (",demofinal$Total[7],")"), paste0(demofinal$Total[9]," (",demofinal$Total[10],")"), demofinal$Total[11]), stringsAsFactors = F
  )
  

```

`r demographicsTotal$total` participants took part in SATIATED, with an equal number in groups AAB and ABB. The groups were similar with respect to intubation attempts (successful or not) undertaken in the previous 12 months. The median number of years as a paramedic was 1.5 years less in group ABB, although the interquartile range was similar. `r demographicsTotal$familiar_SALAD_technique` participants had heard of the SALAD technique prior to the study, with a slightly higher number in group ABB (Table \@ref(tab:demoTable)).


```{r demoTable, echo=F, message=F, warning=F}

  kable(finaldemodf, booktabs=T, format=format, caption="Summary details of participants") %>%
    kable_styling("striped", latex_options = "striped")

```

```{r outcomes, warning=F, message=F, echo=F}

  satiated_data2 <- satiated_data %>%
  mutate(
    # Truncate any overall attempt time greater than 90 seconds to 90 seconds
    attempt1intattemptTotalV = ifelse(attempt1intattemptTotalV > 90, 90, attempt1intattemptTotalV),
    attempt2intattemptTotalV = ifelse(attempt2intattemptTotalV > 90, 90, attempt2intattemptTotalV),
    attempt3intattemptTotalV = ifelse(attempt3intattemptTotalV > 90, 90, attempt3intattemptTotalV),
    # Truncate any intubation time greater than 90 seconds to 90 seconds/
    attempt1intattemptCompletedV = ifelse(attempt1intattemptCompletedV > 90, 90, attempt1intattemptCompletedV),
    attempt2intattemptCompletedV = ifelse(attempt2intattemptCompletedV > 90, 90, attempt2intattemptCompletedV),
    attempt3intattemptCompletedV = ifelse(attempt3intattemptCompletedV > 90, 90, attempt3intattemptCompletedV),
    proportion_successful_intubations = succintattempt/intattempts,
    time_diff_attempt_1_and_2 = attempt1intattemptCompletedV-attempt2intattemptCompletedV,
    time_diff_attempt_1_and_3 = attempt1intattemptCompletedV-attempt3intattemptCompletedV,
    tot_time_diff_attempt_1_and_2 = attempt1intattemptTotalV-attempt2intattemptTotalV,
    tot_time_diff_attempt_1_and_3 = attempt1intattemptTotalV-attempt3intattemptTotalV
  )

  results <- satiated_data2 %>%
  group_by(randomseq) %>%
  summarise(
    n = n(),
    success1and2 = sum(attempt1SuccessV=="yes"&attempt2SuccessV=="yes"),
    success1and3 = sum(attempt1SuccessV=="yes"&attempt3SuccessV=="yes"),
    number_successful_1st_attempt = sum(attempt1SuccessV=="yes"),
    number_successful_2nd_attempt = sum(attempt2SuccessV=="yes"),
    number_successful_3rd_attempt = sum(attempt3SuccessV=="yes"),
    mean_diff_attempt_1_and_2 = mean(time_diff_attempt_1_and_2[attempt1SuccessV=="yes"&attempt2SuccessV=="yes"]),
    mean_diff_attempt_1_and_3 = mean(time_diff_attempt_1_and_3[attempt1SuccessV=="yes"&attempt3SuccessV=="yes"]),
    mean_tot_time_diff_attempt_1_and_2 = mean(tot_time_diff_attempt_1_and_2[attempt1SuccessV=="yes"&attempt2SuccessV=="yes"]),
    mean_tot_time_diff_attempt_1_and_3 = mean(tot_time_diff_attempt_1_and_3[attempt1SuccessV=="yes"&attempt2SuccessV=="yes"]),
    mean_attempt_time_1 = mean(attempt1intattemptCompletedV),
    mean_attempt_time_2 = mean(attempt2intattemptCompletedV),
    mean_attempt_time_3 = mean(attempt3intattemptCompletedV),
    mean_succ_attempt_time_1 = mean(attempt1intattemptCompletedV[attempt1SuccessV=="yes"]),
    mean_succ_attempt_time_2 = mean(attempt2intattemptCompletedV[attempt2SuccessV=="yes"]),
    mean_succ_attempt_time_3 = mean(attempt3intattemptCompletedV[attempt3SuccessV=="yes"]),
    tot_mean_attempt_time_1 = mean(attempt1intattemptTotalV),
    tot_mean_attempt_time_2 = mean(attempt2intattemptTotalV),
    tot_mean_attempt_time_3 = mean(attempt3intattemptTotalV),
    tot_mean_succ_attempt_time_1 = mean(attempt1intattemptTotalV[attempt1SuccessV=="yes"]),
    tot_mean_succ_attempt_time_2 = mean(attempt2intattemptTotalV[attempt2SuccessV=="yes"]),
    tot_mean_succ_attempt_time_3 = mean(attempt3intattemptTotalV[attempt3SuccessV=="yes"])
  )
  
  options(scipen = 999)
  primary_outcome <- tidy(prop.test(results$number_successful_2nd_attempt, results$n ,correct = F))
  
  diffPropPrimary <- primary_outcome$estimate2-primary_outcome$estimate1
  
  AAB <- satiated_data2 %>%
    filter(randomseq == "AAB")
  
  ABB <- satiated_data2 %>%
    filter(randomseq == "ABB")
  
  ### ---- Compare Means of differences -----
  
  # Compare mean time differences of AAB and ABB attempts 1 and 2 i.e. (A01-A02) with (A11-B11)
  tot_meanDiff1and2 <- tidy(t.test(AAB$tot_time_diff_attempt_1_and_2[AAB$attempt1SuccessV=="yes"&AAB$attempt2SuccessV=="yes"], ABB$tot_time_diff_attempt_1_and_2[ABB$attempt1SuccessV=="yes"&ABB$attempt2SuccessV=="yes"]))
  
  meanDiff1and2 <- tidy(t.test(AAB$time_diff_attempt_1_and_2[AAB$attempt1SuccessV=="yes"&AAB$attempt2SuccessV=="yes"], ABB$time_diff_attempt_1_and_2[ABB$attempt1SuccessV=="yes"&ABB$attempt2SuccessV=="yes"]))
  
  sdDiff1and2x <- sd(AAB$tot_time_diff_attempt_1_and_2[AAB$attempt1SuccessV=="yes"&AAB$attempt2SuccessV=="yes"])
  sdDiff1and2y <- sd(ABB$tot_time_diff_attempt_1_and_2[ABB$attempt1SuccessV=="yes"&ABB$attempt2SuccessV=="yes"])
  
  # Compare mean time difference of AAB and ABB attempts 1 and 3 (A01-B01) with (A11-B12)
  tot_meanDiff1and3 <- tidy(t.test(AAB$tot_time_diff_attempt_1_and_3[AAB$attempt1SuccessV=="yes"&AAB$attempt3SuccessV=="yes"], ABB$tot_time_diff_attempt_1_and_3[ABB$attempt1SuccessV=="yes"&ABB$attempt3SuccessV=="yes"]))
  
  meanDiff1and3 <- tidy(t.test(AAB$time_diff_attempt_1_and_3[AAB$attempt1SuccessV=="yes"&AAB$attempt3SuccessV=="yes"], ABB$time_diff_attempt_1_and_3[ABB$attempt1SuccessV=="yes"&ABB$attempt3SuccessV=="yes"]))
  
  sdDiff1and3x <- sd(AAB$tot_time_diff_attempt_1_and_3[AAB$attempt1SuccessV=="yes"&AAB$attempt3SuccessV=="yes"])
  sdDiff1and3y <- sd(ABB$tot_time_diff_attempt_1_and_3[ABB$attempt1SuccessV=="yes"&ABB$attempt3SuccessV=="yes"])
  
  
  ### --- Secondary outcome proportion successfyl on 3rd attempt ----
  
  secondary_outcome <- tidy(prop.test(results$number_successful_3rd_attempt, results$n ,correct = F))
  
  diffPropSecondary <- secondary_outcome$estimate2-secondary_outcome$estimate1
  
  threesig <- function(x, round=1) {
    
    y <- x
    if(round == 1) {
      y <- round(y, 2)
    }
    
    y <- sprintf("%.2f", y)
    
    return(y)
  }


```


First-pass intubation success with and without SALAD on the second attempt, was `r round((primary_outcome$estimate1*100),1)`% vs `r round((primary_outcome$estimate2*100),1)`% respectively, a significant difference of `r round(diffPropPrimary*100,1)`% (95%CI `r paste(round(abs(primary_outcome$conf.high)*100,1),round(abs(primary_outcome$conf.low)*100,1),sep="--")`%, `r ifelse(primary_outcome$p.value < 0.0001, "p<0.0001", threesig(primary_outcome$p.value))`).

```{r times, echo=F, warning=F, message=F}

  timedf <- satiated_data2 %>%
  select(randomseq, attempt1intattemptStartV, attempt2intattemptStartV, attempt3intattemptStartV, attempt1intattemptCompletedV, attempt1intattemptTotalV, attempt2intattemptCompletedV, attempt2intattemptTotalV, attempt3intattemptCompletedV, attempt3intattemptTotalV, attempt1SuccessV, attempt2SuccessV, attempt3SuccessV) %>%
  mutate(
    id = row_number()
  ) %>%
  gather(key, value, -randomseq, -id) %>%
  mutate(
    attempt = as.factor(substr(key,8,8))
  ) %>%
  group_by(id, randomseq, attempt) %>%
  summarise(
    success = ifelse(value[grepl("Success",key)] == "yes", 1, 0),
    time_to_int = as.integer(value[grepl("Start", key)]),
    tot_time = as.integer(value[grepl("Total",key)]),
    int_time = as.integer(value[grepl("Completed",key)])
  )

timedf2 <- timedf %>%
  mutate(
    success = ifelse(success == 1, "Successful Intubation", "Failed Intubation")
  )

# Summary statistics for successful intubations
timedf3 <- timedf %>%
  filter(success==1) %>%
  group_by(attempt, randomseq) %>%
  summarise(
    nsuccess = n(),
    pcsuccess = nsuccess/82,
    medt2int = median(time_to_int),
    medint = median(int_time),
    medtotal = median(tot_time),
    lqtrt2int = fivenum(time_to_int)[2],
    lqtrint = fivenum(int_time)[2],
    lqtrtotal = fivenum(tot_time)[2],
    uqtrt2int = fivenum(time_to_int)[4],
    uqtrint = fivenum(int_time)[4],
    uqtrtotal = fivenum(tot_time)[4]
  )

```

Figure \@ref(fig:boxplotint) summarises the intubation attempt times by participants in each randomisation group. For successful intubation attempts, group ABB was generally faster, except on attempt 2, where AAB intubated sooner (Table \@ref(tab:summarytime).

```{r summarytime, echo=F, warning=F, message=F}

  summarytimedf <- data.frame(
    Measure = c("Successful attempts n (%)", "Median elapsed time to intubation attempt secs (IQR)", "Median intubation attempt time secs (IQR)", "Median total attempt time secs (IQR)"),
    AAB = c(paste0(timedf3$nsuccess[timedf3$attempt==1&timedf3$randomseq=="AAB"], " (",round(timedf3$pcsuccess[timedf3$attempt==1&timedf3$randomseq=="AAB"]*100,1),")"), 
              paste0(timedf3$medt2int[timedf3$attempt==1&timedf3$randomseq=="AAB"]," (", timedf3$lqtrt2int[timedf3$attempt==1&timedf3$randomseq=="AAB"],"--",timedf3$uqtrt2int[timedf3$attempt==1&timedf3$randomseq=="AAB"], ")"),
              paste0(timedf3$medint[timedf3$attempt==1&timedf3$randomseq=="AAB"]," (", timedf3$lqtrint[timedf3$attempt==1&timedf3$randomseq=="AAB"],"--",timedf3$uqtrint[timedf3$attempt==1&timedf3$randomseq=="AAB"], ")"),
              paste0(timedf3$medtotal[timedf3$attempt==1&timedf3$randomseq=="AAB"]," (", timedf3$lqtrtotal[timedf3$attempt==1&timedf3$randomseq=="AAB"],"--",timedf3$uqtrtotal[timedf3$attempt==1&timedf3$randomseq=="AAB"], ")")
  ),
  ABB = c(paste0(timedf3$nsuccess[timedf3$attempt==1&timedf3$randomseq=="ABB"], " (",round(timedf3$pcsuccess[timedf3$attempt==1&timedf3$randomseq=="ABB"]*100,1),")"), 
              paste0(timedf3$medt2int[timedf3$attempt==1&timedf3$randomseq=="ABB"]," (", timedf3$lqtrt2int[timedf3$attempt==1&timedf3$randomseq=="ABB"],"--",timedf3$uqtrt2int[timedf3$attempt==1&timedf3$randomseq=="ABB"], ")"),
              paste0(timedf3$medint[timedf3$attempt==1&timedf3$randomseq=="ABB"]," (", timedf3$lqtrint[timedf3$attempt==1&timedf3$randomseq=="ABB"],"--",timedf3$uqtrint[timedf3$attempt==1&timedf3$randomseq=="ABB"], ")"),
              paste0(timedf3$medtotal[timedf3$attempt==1&timedf3$randomseq=="ABB"]," (", timedf3$lqtrtotal[timedf3$attempt==1&timedf3$randomseq=="ABB"],"--",timedf3$uqtrtotal[timedf3$attempt==1&timedf3$randomseq=="ABB"], ")")
  ),
  AAB = c(paste0(timedf3$nsuccess[timedf3$attempt==2&timedf3$randomseq=="AAB"], " (",round(timedf3$pcsuccess[timedf3$attempt==2&timedf3$randomseq=="AAB"]*100,1),")"), 
              paste0(timedf3$medt2int[timedf3$attempt==2&timedf3$randomseq=="AAB"]," (", timedf3$lqtrt2int[timedf3$attempt==2&timedf3$randomseq=="AAB"],"--",timedf3$uqtrt2int[timedf3$attempt==2&timedf3$randomseq=="AAB"], ")"),
              paste0(timedf3$medint[timedf3$attempt==2&timedf3$randomseq=="AAB"]," (", timedf3$lqtrint[timedf3$attempt==2&timedf3$randomseq=="AAB"],"--",timedf3$uqtrint[timedf3$attempt==2&timedf3$randomseq=="AAB"], ")"),
              paste0(timedf3$medtotal[timedf3$attempt==2&timedf3$randomseq=="AAB"]," (", timedf3$lqtrtotal[timedf3$attempt==2&timedf3$randomseq=="AAB"],"--",timedf3$uqtrtotal[timedf3$attempt==2&timedf3$randomseq=="AAB"], ")")
  ),
    ABB = c(paste0(timedf3$nsuccess[timedf3$attempt==2&timedf3$randomseq=="ABB"], " (",round(timedf3$pcsuccess[timedf3$attempt==2&timedf3$randomseq=="ABB"]*100,1),")"), 
              paste0(timedf3$medt2int[timedf3$attempt==2&timedf3$randomseq=="ABB"]," (", timedf3$lqtrt2int[timedf3$attempt==2&timedf3$randomseq=="ABB"],"--",timedf3$uqtrt2int[timedf3$attempt==2&timedf3$randomseq=="ABB"], ")"),
              paste0(timedf3$medint[timedf3$attempt==2&timedf3$randomseq=="ABB"]," (", timedf3$lqtrint[timedf3$attempt==2&timedf3$randomseq=="ABB"],"--",timedf3$uqtrint[timedf3$attempt==2&timedf3$randomseq=="ABB"], ")"),
              paste0(timedf3$medtotal[timedf3$attempt==2&timedf3$randomseq=="ABB"]," (", timedf3$lqtrtotal[timedf3$attempt==2&timedf3$randomseq=="ABB"],"--",timedf3$uqtrtotal[timedf3$attempt==2&timedf3$randomseq=="ABB"], ")")
  ),
    AAB = c(paste0(timedf3$nsuccess[timedf3$attempt==3&timedf3$randomseq=="AAB"], " (",round(timedf3$pcsuccess[timedf3$attempt==3&timedf3$randomseq=="AAB"]*100,1),")"), 
              paste0(timedf3$medt2int[timedf3$attempt==3&timedf3$randomseq=="AAB"]," (", timedf3$lqtrt2int[timedf3$attempt==3&timedf3$randomseq=="AAB"],"--",timedf3$uqtrt2int[timedf3$attempt==3&timedf3$randomseq=="AAB"], ")"),
              paste0(timedf3$medint[timedf3$attempt==3&timedf3$randomseq=="AAB"]," (", timedf3$lqtrint[timedf3$attempt==3&timedf3$randomseq=="AAB"],"--",timedf3$uqtrint[timedf3$attempt==3&timedf3$randomseq=="AAB"], ")"),
              paste0(timedf3$medtotal[timedf3$attempt==3&timedf3$randomseq=="AAB"]," (", timedf3$lqtrtotal[timedf3$attempt==3&timedf3$randomseq=="AAB"],"--",timedf3$uqtrtotal[timedf3$attempt==3&timedf3$randomseq=="AAB"], ")")
  ),
    ABB = c(paste0(timedf3$nsuccess[timedf3$attempt==3&timedf3$randomseq=="ABB"], " (",round(timedf3$pcsuccess[timedf3$attempt==3&timedf3$randomseq=="ABB"]*100,1),")"), 
              paste0(timedf3$medt2int[timedf3$attempt==3&timedf3$randomseq=="ABB"]," (", timedf3$lqtrt2int[timedf3$attempt==3&timedf3$randomseq=="ABB"],"--",timedf3$uqtrt2int[timedf3$attempt==3&timedf3$randomseq=="ABB"], ")"),
              paste0(timedf3$medint[timedf3$attempt==3&timedf3$randomseq=="ABB"]," (", timedf3$lqtrint[timedf3$attempt==3&timedf3$randomseq=="ABB"],"--",timedf3$uqtrint[timedf3$attempt==3&timedf3$randomseq=="ABB"], ")"),
              paste0(timedf3$medtotal[timedf3$attempt==3&timedf3$randomseq=="ABB"]," (", timedf3$lqtrtotal[timedf3$attempt==3&timedf3$randomseq=="ABB"],"--",timedf3$uqtrtotal[timedf3$attempt==3&timedf3$randomseq=="ABB"], ")")
  ), check.names = F
  )


  kable(summarytimedf, booktabs=T, format=format, caption="Summary data of successful intubation attempts") %>%
    kable_styling("striped", latex_options = "striped") %>%
    column_spec(1, width = "4cm") %>%
    add_header_above(c(" " = 1, "Attempt 1" = 2, "Attempt 2" = 2, "Attempt 3" = 2))

```


```{r boxplotint, message=F, echo=F, warning=F, fig.cap="Intubation attempt times, stratified by randomisation sequence and intubation success"}

ggplot(timedf2, aes(x = attempt, y = int_time, fill=randomseq)) +
  geom_boxplot() +
  facet_wrap(~success) +
  theme_minimal() +
  theme(legend.position="top") +
  scale_fill_brewer(name="Randomisation group") +
  scale_y_continuous(name="Intubation attempt time (seconds)", breaks = seq(0,90,10), limits=c(20,90)) +
  scale_x_discrete(name="Attempt number")

```

```{r mdTable, message=F, warning=F, echo=F}

  attemptDiff <- satiated_data2 %>%
    mutate(
      class1_2 = ifelse(attempt1SuccessV == "yes", ifelse(attempt2SuccessV=="yes","SS","SF"), ifelse(attempt2SuccessV=="yes","FS","FF")),
      class1_3 = ifelse(attempt1SuccessV == "yes", ifelse(attempt3SuccessV=="yes","SS","SF"), ifelse(attempt3SuccessV=="yes","FS","FF"))
    ) %>%
    select(randomseq, class1_2, class1_3, time_diff_attempt_1_and_2, time_diff_attempt_1_and_3) %>%
    filter(class1_2 == "SS" | class1_3 == "SS") %>%
    gather(key, value, -randomseq, -class1_2, -class1_3) %>%
    mutate(
      one2two = ifelse(class1_2 == "SS" & key == "time_diff_attempt_1_and_2", value, NA),
      one2three = ifelse(class1_3 == "SS" & key == "time_diff_attempt_1_and_3" , value, NA)
    ) %>%
    select(randomseq, one2two, one2three) %>%
    gather(key, value, -randomseq) %>%
    na.omit()

lotsmeans <- attemptDiff %>%
  group_by(key, randomseq) %>%
  summarise(
    n = n(),
    mean = mean(value),
    sd = sd(value)
  ) %>%
  mutate(se = sd / sqrt(n),
         lower.ci = mean - qt(1 - (0.05 / 2), n - 1) * se,
         upper.ci = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
  mutate_if(is.numeric, round, 1)

```


## Mean difference in successful intubation attempts

```{r lotsmeans, echo=F, warning=F, message=F}
  
  lotsmeans2 <- lotsmeans[c(3,4,1,2),-1] %>%
  mutate(
    ci = paste0(lower.ci, "--",upper.ci)
  ) %>%
  select(-lower.ci, -upper.ci)

  colnames(lotsmeans2) <- c("group", "n", "mean difference (secs)", "standard deviation (secs)", "standard error (secs)", "95% CI")
  
  kable(lotsmeans2, booktabs=T, format=format, caption="Summary data of successful intubation attempts") %>%
      kable_styling("striped", latex_options = "striped", full_width = F) %>%
      group_rows("Attempts 1 and 2", 1, 2) %>%
      group_rows("Attempts 1 and 3", 3, 4)

```


 There was a significant difference between groups AAB (n=`r results$success1and2[results$randomseq=="AAB"]`) and ABB (n=`r results$success1and2[results$randomseq=="ABB"]`) with respect to the mean difference in time taken to perform a successful intubation on attempts 1 and 2 (mean difference `r threesig(meanDiff1and2$estimate)` seconds, 95% CI `r threesig(meanDiff1and2$conf.low)`--`r threesig(meanDiff1and2$conf.high)` seconds, p=`r threesig(meanDiff1and2$p.value)`). There was no significant difference between groups AAB  (n=`r results$success1and3[results$randomseq=="AAB"]`) and ABB (n=`r results$success1and3[results$randomseq=="ABB"]`) with respect to mean difference in time taken to perform a successful intubation on attempts 1 and 3 (mean difference  `r threesig(meanDiff1and3$estimate)` seconds, 95% CI `r threesig(meanDiff1and3$conf.low)`--`r threesig(meanDiff1and3$conf.high)` seconds, p=`r threesig(meanDiff1and3$p.value)`)). Summary values for the mean differences are shown in Table \@ref(tab:lotsmeans). Finally, there was no significant difference in success rates on the third attempt between AAB and ABB `r round((secondary_outcome$estimate2*100),1)`% vs `r round((secondary_outcome$estimate1*100),1)`% respectively, a difference of `r round(diffPropSecondary*100,1)`% (95%CI `r paste(round(abs(secondary_outcome$conf.high)*100,1),round(abs(secondary_outcome$conf.low)*100,1),sep="--")`%, p=`r threesig(secondary_outcome$p.value)`).
 
 
```{r techniquePrep, error=F, message=F, warning=F, echo=F}

  summaryExtras <- satiated_data2 %>%
  group_by(randomseq) %>%
  summarise(
    bougie1 = sum(!is.na(bougie1)),
    bougie2 = sum(!is.na(bougie2)),
    bougie3 = sum(!is.na(bougie3)),
    assthold1 = sum(!is.na(assthold1)),
    assthold2 = sum(!is.na(assthold2)),
    assthold3 = sum(!is.na(assthold3)),
    sucinsitu1 = sum(!is.na(sucinsitu1)),
    sucinsitu2 = sum(!is.na(sucinsitu2)),
    sucinsitu3 = sum(!is.na(sucinsitu3)),
    nohole1 = sum(!is.na(Nohole1)),
    nohole2 = sum(!is.na(Nohole2)),
    nohole3 = sum(!is.na(Nohole3))
  )

summaryExtras2 <- summaryExtras %>%
  gather(key, value, -randomseq) %>%
  mutate(
    attempt = str_sub(key, -1, -1),
    new_key = str_sub(key, 1, -2)
  ) %>%
  select(randomseq, new_key, value, attempt) %>%
  mutate(
    attempt = paste("Attempt ", attempt, sep=" ")
  )

  bougieProbe <- satiated_data2 %>%
  select(bougie1, bougie2, bougie3, randomseq, attempt1SuccessV, attempt2SuccessV, attempt3SuccessV) %>%
  mutate(
    id = row_number()
  ) %>%
  gather(key, value, -randomseq, -id) %>%
  mutate(
    attempt = as.factor(ifelse(str_sub(key, 1, 6) == "bougie", str_sub(key,7,7) , substr(key,8,8)))
  ) %>%
  group_by(id, randomseq, attempt) %>%
  summarise(
    success = ifelse(value[grepl("Success",key)] == "yes", 1, 0),
    bougie = ifelse(is.na(value[grepl("bougie", key)]), 1, 0)
  ) %>%
  ungroup() %>%
  select(success, bougie) %>%
  count(success, bougie)


```
 
## Technique

A number of techniques were utilised by participants to facillitate intubation (Figure \@ref(fig:techniqueBarchart)). This included asking the assistant to hold the suction catheter in the mouth (n=`r sum(summaryExtras2$value[summaryExtras2$new_key=="assthold"])`), and leaving with the suction in the mouth (although without occluding the suction vent hole, n=`r sum(summaryExtras2$value[summaryExtras2$new_key=="nohole"])`). In addition, there were also instances where participants did not use a bougie (n=`r sum(summaryExtras2$value[summaryExtras2$new_key=="bougie"])`, of which `r bougieProbe$n[1]` were successful attempts, and `r bougieProbe$n[3]` unsucessful) and forgot to occlude the suction vent hole on the catheter when attempting to clear the airway themselves (n=`r sum(summaryExtras2$value[summaryExtras2$new_key=="sucinsitu"])`).
 
 
```{r techniqueBarchart, warning=F, message=F, echo=F, fig.cap="Bar chart showing techniques and omissions during intubation attempts, stratified by randomisation group and attempt number", fig.width=7}

  ggplot(summaryExtras2, aes(x = new_key, y = value, fill = randomseq)) +
  geom_bar(stat = "identity", position="dodge", colour="black") +
  facet_wrap(~attempt) +
  theme_minimal() +
  theme(legend.position="top") +
  scale_fill_brewer(name="Randomisation group") +
  scale_y_continuous(name="Number of occurances", breaks = seq(0,15,1), limits=c(0,15)) +
  scale_x_discrete(name="Technique adaptions/omissions", labels=c("Assistant\nheld\nsuction", "No bougie\nused", "Suction\nhole not\noccluded", "Suction left\nin situ"))

```
 
 
 
 